---
title: "runoff_volumes"
author: "Javier Patron"
date: "2022-08-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(here)
```

Source your storm_runoff.R script so you are able to use the predict_runoff function in your .Rmd

```{r}
source(here::here("src","storm_runoff.R"))
predict_runoff(1,2)

```


Estimate stormwater volume for a watershed of 182 acres, over a range of estimates for the impervious fraction (from 0.6 to 0.8, by increments of 0.01).


```{r}

imp_frac <- seq(from = 0.6, to = 0.8, by = 0.01)

results <- predict_runoff(imp_frac,182)


```

Bind your sequence of impervious fractions together with the resulting runoff volume calculated into a data frame

```{r}
df <- data.frame(resulting_runoff = c(results), sequence = c(imp_frac))
```

Graph

```{r}
graph <- ggplot(data = df, aes(x = resulting_runoff, y = sequence)) + 
  geom_line() + 
  geom_point() + 
  labs (title = "Predict Runoff", x = "Resulting Runoff", y = "Sequence")
```


Save your graph
```{r}

ggsave(plot = graph, here::here("figs", "predict_runoff.png"))
```




TASK 2

```{r}



```

